Agents and you, a brief summary

### 2015-11-03 agents/summery.tex
added all the belman and markov things, going on to modal logics.

\[ \Pi = max_{\pi \in \Pi}(payoff(\pi))\]

@@

\subsection{Utility pumps}
If there is no discount factor policy is irrelivant (the reward will be
infinite no matter what you do). A tool is needed to kill infinity.
For example a finiti horizon, discount factor, or long-run average
payoffs.

@@

@@

>>>>

\[ \Pi = argmax_{\pi \in \Pi}(payoff(\pi))\]

@@

\paragraph{Utility pumps}
If there is no discount factor policy is irrelivant (the reward will be
infinite no matter what you do). A tool is needed to kill infinity.
For example a finiti horizon, discount factor, or long-run average
payoffs.

@@

\paragraph{Investment} 
At cycle $a$, it is possible to `pump' 1 utitlity per iteration for as
long as a run lasts. At cycle $b$ it is possbile to `pump' $2$ utilities
per iteration.
In the long term it is better to be at $b$, but starting from $a$ this
requires an investment of $K$ rewardless transitions to get there.

\begin{center}
\begin{tikzpicture}[->, >=stealth', auto, semithick, node distance=3cm]
\tikzstyle{every state}=[fill=white,draw=black,thick,text=black,scale=1]
\node[state]    (S)                     {s};
\node[state]    (A)[right of=S]   {$b_1$};
\node[state]    (B)[right of=A]   {$b_{k-1}$};
\node[state]    (C)[right of=B]   {$b_k$};
\path
(S) edge[loop above]     	node{1}(S)
    edge[above]     		node{0}(A)
(A)    edge[above]    node{0}(B)
(B)    edge[above]     		node{0}(C)
(C)    edge[loop above]		node{1}(C);
\end{tikzpicture}
\end{center}

If $K \ne 0$ it is best to stay left if $\gamma < 2^{-1/k}$. (for the
proof see the slides, its to much math to copy in here).

\subsection{Policy improvement}

Recall the bellman equations for a Markov reward process:

\[ v = C+\gamma P v\]

To emphasise that $v$ depends on a probability transition matrix $P$:

\[ v^P = C^P + \gamma P v^P\]

In a \emph{decision problem}, $P$ is not chosen by nature, but by a 
\emph{decision maker}. In that case, $P$ is called a \emph{ixed Markov
policy}. and is denoted by $\pi$:

\[ v^\pi = C^\pi + \gamma P^\pi v^\pi\]

Each policy $\pi$ gives a value function $v^\pi$. THe objective is to find a
policy $\pi$ that maximises the value function $v^\pi$.

\subsubsection{First sketch}
A first sketch of a policy iteration algorithm:
\begin{enumerate}
	\item Start with an arbitrary policy $\pi$
	\item Compute $V_\pi$. (know as \emph{policy evaluation}).
	\item Improve $\pi$ locally to $\tau$.
	\item If $\tau \ne \pi$, then $\pi := \tau$, and go to 2.
	\item $\pi$ is optimal.
\end{enumerate}

\paragraph{Problem} Therer are to many ways to improve a policy.
For example if a state $s$ enables two actions, then any
mixed policy $(p, 1-p)$ may be tried locally. This gives
uncountably many (i.e., $|\mathbb{R}|$) alternatives!

Fortunally for discounted decision problems, locl search can be
restricted to pure policies only.

Let $\pi$ be apossibly mixed policy. For each state choose a decision
that is locally maximal:

% I'm not sure where the J is supposed to go.
\[M(i) \in argmax\{r_{ij} + \gamma V_\pi(j)\} \]

Define the pure policy:

\[ \tau_{ij} =_{Def} \delta_{M(i),j} \]

Then $\tau$ is a global improvement of $\pi$.

\subsubsection{Partial correctness}

Correctness  partial correctness + termination.

Partial correctness means: correct if the algrotihm terminates.
\emph{Policy iteration is partially correct:} any strict
local improvement induces a global improvment.
\emph{Policy iteration terminates:} each time a policy is improved,
the new policy is strictly better than the previous.

\subsection{Bellman optimallity}

If $\pi$ is optimal, it follows from the policy improvement thearom that

\[ V^\pi(i) = \underset{all\mbox{\ }j}{max}[r_{ij} + \gamma V^\pi(j)] \]

Removing explicit reference to the optimal policy automatically (more elegant).

\subsubsection{operator}
%seriously what is meant with operator?

% I'm assuming he means with exact the algebraic method and
% the aproximation is the itteration method.
For both methods (the exact as well as the approximation method),
a compacter notation is needed.

\[B: \mathbb{R}^n \to \mathbb{R}^n : v \mapsto
	\underset{all\mbox{\ }j}{max}[C_j + \gamma V(j)] \]

Where $C_j$ is the vector of rewards that emanate from state $i$.
Antoher way to write $B:$
\[\underset{all\mbox{\ }j}{max}[r_{ij} + \gamma V(j)] \]

$B$ does not depend on a policy or transition matrix. ($B_p$ does.)

\subsubsection{Fixed point}
The value-vector, $v^*$, of a decision problem is a fixed point of the
$B$-operator:
\[ B(v) = v\]

@@

% That's all she wrote.
